Supplementary Material

### 2022-08-10 article.tex
Further revisions

Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}. Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}. The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors. These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020,Sullender.2022} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.

@@

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Li:2014ca,Zeng.2014}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system, both of which are necessary for LSCI characterization measurements.

@@

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for one hour, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23 gauge blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end fully submerged in liquid (see Supplementary Material S1). A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.

@@

The syringe pump system (74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run a predefined flow profile, using the 14.5 mm inner diameter of the syringe to ensure a correct flow rate. It should be noted that a 3 mL syringe was also evaluated, however its performance was worse than the 10 mL syringe and could not hold sufficient volume for all trials without being refilled.

@@

The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp}. The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements. This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline. As seen in Fig. \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI. While MESI exhibited slightly more variability during individual flow profile steps (Fig. \ref{fig:flow_mesi_lsci}a), this was likely caused by the fitting process required to calculate $\tau_c$. Numerical artifacts introduced by this nonlinear fitting could also be responsible for the increased error seen with MESI at flow speeds between 3.5 to 6 mm/s. It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located. Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.

@@

This paper demonstrates that flow control system selection is critical for reliably generating flow for microfluidic studies. While ubiquitous in the LSCI community, syringe pumps suffer from poor stability and repeatability that limit their ability to properly characterize the flow sensitivity of optical imaging systems. We show that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of MESI or LSCI with microfluidics. We determine that the uncertainty in flow generation with a pressure-regulated flow system is considerably less than that of a syringe pump system across a range of physiologically-relevant flow speeds. We use the pressure-regulated flow system to further demonstrate the superiority of MESI compared to traditional single-exposure LSCI. Using an inline flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively. Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than systematic error. Overall, these results indicate that highly accurate flow control is necessary for reliable characterization of a MESI or LSCI system.

@@

\vspace{2ex}\noindent\textbf{Adam Santorelli} is a research associate at the University of Texas at Austin. He received his B.Eng., M.S.E., and Ph.D. in Electrical Engineering from McGill University. He was an IRC Government of Ireland Postdoctoral Fellow in the Translational Medical Device Lab at the National University of Ireland, Galway from 2017 to 2019. His current research is focused on the translational aspects of speckle imaging.

>>>>

Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can create full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}. Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}. The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors. These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020,Sullender.2022} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.

@@

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over twenty LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Li:2014ca,Zeng.2014}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system, both of which are necessary for LSCI characterization measurements.

@@

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) approximates the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for one hour, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23 gauge blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole-Parmer Instrument Company, LLC) was connected to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC). The outlet tubing drained into a vial, with the tubing end fully submerged in liquid (see Supplementary Material S1). A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.

@@

The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run a predefined flow profile, using the 14.5 mm inner diameter of the syringe to ensure a correct flow rate. It should be noted that a 3 mL syringe was also evaluated, however its performance was worse than the 10 mL syringe and could not hold sufficient volume for all trials without being refilled.

@@

The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp}. The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements. This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline. As seen in Fig. \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI. While MESI exhibited slightly more variability during individual flow profile steps (Fig. \ref{fig:flow_mesi_lsci}), this was likely caused by the fitting process required to calculate $\tau_c$. Numerical artifacts introduced by this nonlinear fitting could also be responsible for the increased error seen with MESI at flow speeds between 3.5 to 6 mm/s. It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located. Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.

@@

This paper demonstrates that flow control system selection is critical for reliably generating flow for microfluidic studies. While ubiquitous in the LSCI community, syringe pumps suffer from poor stability and repeatability that limit their ability to properly characterize the flow sensitivity of optical imaging systems. We show that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of MESI or LSCI with microfluidics. We determine that the uncertainty in flow generation with a pressure-regulated flow system is considerably less than that of a syringe pump system across a range of physiologically-relevant flow speeds. We use the pressure-regulated flow system to further demonstrate the superiority of MESI compared to traditional single-exposure LSCI. Using an inline flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively. Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than systematic error. Overall, these results indicate that highly accurate flow control is necessary for the reliable characterization of a MESI or LSCI system.

@@

\vspace{2ex}\noindent\textbf{Adam Santorelli} is a research associate at the University of Texas at Austin. He received his B.Eng., M.S.E., and Ph.D. in Electrical Engineering from McGill University. He was an IRC Government of Ireland Postdoctoral Fellow in the Translational Medical Device Lab at the National University of Ireland, Galway. His current research is focused on the translational aspects of speckle imaging.

### 2022-08-10 supplement.tex
Further revisions

% Figure S1 - Outlet Line Submersion
\begin{figure}
    \includegraphics[width=\textwidth]{FigureS1.pdf}
    \caption {
        Impact of submerging the microfluidic device outlet tubing for both flow control systems at 2.4 and 4.8 mm/s as measured with the inline flow sensor (blue) and single-exposure LSCI (red). These trials show approximately five minutes of effluent dripping into the collection vial, as evidenced by the periodic flow decreases, followed by five minutes of operation with the outlet tubing submerged in the collected solution. The large spike in relative flow around $t = $ 300 seconds corresponds to the outlet line being manually submerged in solution. All measurements were normalized to the average flow during the submerged segment of each trial and compared to the ideal flow (black).
    }
    \label{fig:supplement_outlet}
\end{figure}

>>>>

% Figure S1 - Outlet Line Submersion
\begin{figure}
    \includegraphics[width=\textwidth]{FigureS1.pdf}
    \caption {
        Impact of submerging the microfluidic device outlet tubing for both flow control systems at 2.4 and 4.8 mm/s as measured with the inline flow sensor (blue) and single-exposure LSCI (red). These trials show approximately five minutes of effluent dripping into the collection vial, as evidenced by the periodic flow decreases, followed by five minutes of operation with the outlet tubing submerged in the collected solution. The large spike in relative flow around $t = $ 300 seconds corresponds to the outlet line being manually submerged in the solution. All measurements were normalized to the average flow during the submerged segment of each trial and compared to the ideal constant flow (black).
    }
    \label{fig:supplement_outlet}
\end{figure}
